Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-05 article.tex
HLAs described better

@@

Any human's immune system detects only a fraction of all possible
polypeptide fragments. 
Already each MHC molecule can only bind a
subset of all possible polypeptides (but it has been observed 
that HLA-A and HLA-B have no overlap in which
peptides they bind, \cite{lund2004definition}).
The classification of HLAs is based on algorithms that
maximize the information content of each 
classification, such as the presence of a certain amino acid at 
the first (for MHC-II, \cite{southwood1998several})
or second position (for MHC-I, \cite{lund2004definition}) of a polypeptide.
However, this does not imply that all polypeptides for a classification
pattern bind to the MHC, as there is no simple method to predict which 
MHCs bind which epitopes.
Using artificial neural networks, it became
possible to make theoretical predictions \cite{nielsen2003reliable,nielsen2004improved},
which are tested to be reliable in practice \cite{larsen2010identification,schellens2008unanticipated,tang2011genome}.

We can predict epitopes.
For MHC-I, \verb;epitope-prediction; is used \richel{Cite Johannes}.
For MHC-II, NetMHCIIpan uses all haplotypes \richel{Cite Morten}.
Although \cite{zhang2015accurate} looks like an even better
method for MHC-II, they only take one haplotype into account.

@@

>>>>

\paragraph{Classification of HLA}

Any human's immune system detects only a fraction of all possible
polypeptide fragments. 
Human MHCs are also called HLAs ('Human Leukocyte Antigens') and
because this research uses human hosts only, we will use these terms
interchangeably.
Already each MHC molecule can only bind a, possible exclusive,
subset of all possible polypeptides.
For example, HLA-A and HLA-B have no overlap in which
peptides they bind (\cite{lund2004definition}).
The HLA region of humans is highly polymorphic, 
making it hard to classify all of the many haplotypes.
Classification of HLAs is based on algorithms that
maximize the information content of each 
classification, such as the presence of a certain amino acid at 
the first (for MHC-II, \cite{southwood1998several})
or second position (for MHC-I, \cite{lund2004definition}) of a polypeptide.
However, this does not imply that all polypeptides for a classification
pattern bind to the MHC. Instead, software should be used that are
tailored to predict if a polypeptide binds to an HLA.

@@

It is helpful to be able to predict which polypeptides are immunogenic,
in, among others, vaccine development \richel{Reference here}. 
Already for a decade, synthesized polypeptide fragments are used 
to experimentally determine which polypeptides
are immunogenic \richel{Reference here}.
This approach, however, is tedious and costly.
It should come as no surprise that these results would be used
to make in silico predictions.
It may come as a surprise, however, that these predictions
are actually reliable in practice \cite{larsen2010identification,schellens2008unanticipated,tang2011genome}.

\paragraph{MHC-I epitope prediction}

For MHC-I, there are multiple computational tools developed 
to predict epitopes. 
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCcons \cite{karosiene2012netmhccons} gave the best predictions.
A tool not included in this review is \verb;epitope-prediction;,
which uses a stabilized matrix method, as described in \cite{kim2009derivation}.
The reason this tool is mentioned, is because it is used 
in cite{bianchi2017}.

\paragraph{MHC-II epitope prediction}

Also for MHC-II, there are multiple computational tools developed 
to predict epitopes,
such as using a trained neural network (\cite{nielsen2003reliable})
or a Gibbs sampling approach (\cite{nielsen2004improved}).
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCIIpan (\cite{nielsen2008quantitative,karosiene2013netmhciipan})
gave rise to the most accurate predictions.
Later tools are \cite{zhang2013predicting},
\cite{trolle2014nettepi} and \cite{zhang2015accurate}.
These later tools, although they look promising, have not been compared
with one another \richel{Maybe cool to do so!}.

\paragraph{Leftovers (to move or remove)}

@@

\paragraph{TMH prediction}

\richel{Or someplace else. Reorganise!}
